Figures and tables for paper

### 2021-09-21 analysis/04_figs-tables.Rmd
Contrasts pt.1

## Plot contrasts

>>>>

## Plot contrasts
```{r}

# Organization Intercept Contrasts

draws_A <- subset(intercept, i==1, select = Gamma)
draws_G <- subset(intercept, i==2, select = Gamma)
draws_O <- subset(intercept, i==3, select = Gamma)
draws_R <- subset(intercept, i==4, select = Gamma)
draws_con <- tibble(
  "A-G" = draws_A-draws_G,
  "A-O" = draws_A-draws_O,
  "A-R" = draws_A-draws_R,
  "G-O" = draws_G-draws_O,
  "G-R" = draws_G-draws_R,
  "O-R" = draws_O-draws_R
)

c1 <- bind_rows(draws_con$`A-G`, draws_con$`A-O`)
c1 <- bind_rows(c1, draws_con$`A-R`)
c1 <- bind_rows(c1, draws_con$`G-O`)
c1 <- bind_rows(c1, draws_con$`G-R`)
c1 <- bind_rows(c1, draws_con$`O-R`)

c1$code[1:2000] <- 1
c1$code[2001:4000] <- 2
c1$code[4001:6000] <- 3
c1$code[6001:8000] <- 4
c1$code[8001:10000] <- 5
c1$code[10001:12000] <- 6

lcon <- c("A-G", "A-O", "A-R", "G-O", "G-R", "O-R")
ggplot(c1, aes(x=Gamma)) +
    stat_halfeye(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels") + facet_wrap(~code)
```
